\input kpreamble


\begin{document}

\title{231B: Spin statistics and multi-electron atoms}
\author{Quiz 3, Winter 2020}
\date{\today}
\maketitle

\begin{enumerate}

\item For a potential $V(x)$ with only two bound states, one at -10 eV
and the other at -2 eV, what is the ground-state energy of two ideal
fermions in the well, and what is its spin state?

\item What is the energy and degeneracy of the first excited state for the previous
problem?

\item For 4 ideal fermions in the well above, what is the ionization potential?

\item Write the Hartree-Fock ground-state wavefunction for two electrons in a He atom in terms
of its atomic orbitals and spin states.

\item Write the Hamiltonian for the three electrons in the Li atom.

\item When adding two angular momenta, each with $j=1$, list all the allowed
values of $J$ and $M$, the quantum numbers for their sum, and give the total number of states.

\item In the previous problem, write the formula relating the $|J,M>$
state at the top
of the ladder with its equivalent representation in terms of the
product of individual states, $|m_1,m_2>$.

\item The ground-state Hartree-Fock energy for He is $-77.9$ eV.  What statement can
you make with absolute confidence about the ionization potential of He?

\item The Hartree-Fock eigenvalue for the 1s orbital in He is $-24.9$ eV.  Compare
this with previous question to give the error in Koopmans' theorem.

\item The allowed terms for the three $p$-electrons in N are $^2P, ^2D$, and $^4S$.
Give the order of their energies (say which is lowest, in the middle, and highest).


\end{enumerate}
\end{document}
